`flippant` -- An `R` package for the automated analysis of dithionite scramblase

### 2015-09-24 inst/manuscript/manuscript.rmd
Try to robustify nlmrt-calls further by additional garbage collection;

#Conclusion
```{r, echo = FALSE, cache = TRUE}
setwd(tmpDir)
analysis_timing_n <- 100
analysis_timing_function <- function(){
  scramblaseAssayTraces(
    "inputTable.txt",
    timeMax = 350)
  scramblaseAssayPlot("inputTable.txt")
  scramblaseAssayStats("inputTable.txt")
}
analysis_timing <- microbenchmark(
  analysis_timing_function(),
  times = analysis_timing_n)

>>>>

#Conclusion
```{r, echo = FALSE, cache = TRUE}
setwd(tmpDir)
analysis_timing_n <- 100
analysis_timing_function <- function(){
  scramblaseAssayTraces(
    "inputTable.txt",
    timeMax = 350)
  scramblaseAssayPlot("inputTable.txt")
  scramblaseAssayStats("inputTable.txt")
  gc()
}
analysis_timing <- microbenchmark(
  analysis_timing_function(),
  times = analysis_timing_n)
